---
title: "MyBlog"
author: "PT"
date: "2023-01-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
# install_hugo()
blogdown::install_hugo(arch = 'universal')
```

## Hugo

Hugo theme on github and you can optionally specify a GIT branch or tag name after @, theme can be of the form 
user/repo@branch
when the new site is ready:
1. To start a local preview: use blogdown::serve_site(), or the RStudio add-in "Serve Site"
2. To stop a local preview: use blogdown::stop_server(), or restart your R session

```{r}
library(blogdown)
# blogdown::hugo_version()
blogdown::new_site(theme = "gurusabarish/hugo-profile", force = T)
```

## some tips
config.toml has the global settings for the site in the source pane
manage changes with Git
1. check the status of the files in your project `git status`
2. Add the files to be tracked: `git add .`
3. command file changes: if you want to commit these changes, use `git commit -m "first commit"`
4. Push files to github:  `github`

## Create new posts
The new posts go in the `content` folder, can create new post using the Addins: click on New Post
Then, choose to use .Rmd file
You can use `insert image` option under the Addins

## Next
After finishing, we need to manage the changes with Git. 
1. git status check 
2. Add changes using the Git pane (clicking the small checkbox and then clicking commit)
3. step 2 opens Rstudio's Git management window. I enter a message in the Commit message window, and then click commit, and watch the changes get tracked

## Next
1. change have been committed, see how things look on the website: blogdown::serve_site()
2. repeat Git processes -> make sure push these changes to Github repository
3. click on the Push icon and waiting for the message to tell changes have been pushed to Github (HEAD->master)


